\subsection{Task 5: Project and User attachment}\label{sec:project}

\begin{note}
For this task, please write all your code in the file \texttt{project.yaml}
at the root of the \texttt{workshop/} directory.
\end{note}

\subsubsection{Project}

Finally, you can declare a project resource.
In order to create the resource you will need to import some flavor and images to 
create a kubernetes cluster or a vm.
In our case we will create a kubernetes cluster so we just need flavors.

\begin{tip}
Please read the this \href{https://itera.gitbook.io/taikun/guidelines/creating-a-cluster}{page}.
It explains how to create a cluster with Taikun and what are the needed resources.
\end{tip}


Now it is your turn to create the project with the resources we created in 
the previous tasks.
You can use reference arguments because all the resources needed have been created in your 
\texttt{crossplane-system} namespace in your cluster.

You can found \href{https://github.com/itera-io/provider-jet-taikun/blob/main/docs/project.taikun.jet.crossplane.io.md}{here}
 the project resource documentation.

\subsubsection{Project User Attachment}

Now, as you just write the configuration file your project, you can assign
 users to your project.
The users you want to attach to the project must be in the same organization.
 In our case the 
resources must belong to the organization created in \fullref{sec:organization}.

So see to the Project User Attachment \href{https://github.com/itera-io/provider-jet-taikun/blob/main/docs/projectuserattachment.taikun.jet.crossplane.io.md}{documentation} 
here andafter writing the two resources in \texttt{project.yaml} you can apply 
your file.

